Fusion Moves for Correlation Clustering

### 2014-11-10 paper/egpaper_for_review.tex
update plots
mystuff

@@

@@

Fusion moves as defined in \cite{Lempitsky-2010} work
in the node domain and do not work properly for 
objective functions as Eq.~\ref{eq:nodeproblem} since
the node coloring is ambiguous and has no semantic meaning.
In the following, we propose a more suitable fusion move for correlation
clustering which works on the edge domain.
%
Given two proposal solutions $y'$ and $y''$,
$\mathcal{C}$ is the set of edges
which are uncut in $y'$ and $y''$.

\begin{align}
\breve{y}    & =  y' \cup y'' \\
\mathcal{C}  & =  \{ (i, j) \quad | \quad \breve{y}_{ij} = 0 \}
\end{align}

The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
with additional \emph{must-link constraints} for all edges in $\mathcal{C}$.

\begin{align}
  y^* &=& \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:fusion_move_a}.\\ 
  s.t & &  y_{ij} = 0 \quad \forall (i, j) \in \mathcal{C} \nonumber
\end{align}

By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy:
\begin{align}
  \sum  w_{ij} \cdot y^*_{ij}  \leq \min \left( \sum  w_{ij} \cdot y'_{ij} ,  \sum   w_{ij} \cdot y''_{ij} \right)
\end{align}

Eq.~\ref{eq:fusion_move_a} can be solved efficiently, since 
we can work on a coarser graph, where all nodes which are connected
via must-link constraints are merged into single nodes.
This coarser graph is constructed by contracting all must-link edges.

>>>>

% Two Colored Circle Split 
\makeatletter
\tikzset{circle split part fill/.style  args={#1,#2}{%
 alias=tmp@name, 
  postaction={%
    insert path={
     \pgfextra{% 
     \pgfpointdiff{\pgfpointanchor{\pgf@node@name}{center}}%
                  {\pgfpointanchor{\pgf@node@name}{east}}%            
     \pgfmathsetmacro\insiderad{\pgf@x}
      \fill[#1] (\pgf@node@name.base) ([xshift=-\pgflinewidth]\pgf@node@name.east) arc
                          (0:180:\insiderad-\pgflinewidth)--cycle;
      \fill[#2] (\pgf@node@name.base) ([xshift=\pgflinewidth]\pgf@node@name.west)  arc
                           (180:360:\insiderad-\pgflinewidth)--cycle;            
         }}}}}  
 \makeatother

@@

\input{inputs/fig_fusion.tex}

@@

Fusion moves as defined in \cite{Lempitsky-2010} work
in the node domain and do not work properly for 
objective functions as Eq.~\ref{eq:nodeproblem} since
the node coloring is ambiguous and has no semantic meaning.
In the following, we propose a more suitable fusion move for correlation
clustering which works on the edge domain.
%
Given two proposal solutions $y'$ and $y''$,
$\mathcal{C}$ is the set of edges
which are uncut in $y'$ and $y''$.
%
\begin{align}
\breve{y}    & =  y' \cup y'' \\
\mathcal{C}  & =  \{ (i, j) \quad | \quad \breve{y}_{ij} = 0 \}
\end{align}
%
The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
with additional \emph{must-link constraints} for all edges in $\mathcal{C}$.
%
\begin{align}
  y^* &=& \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:fusion_move_a}.\\ 
  s.t & &  y_{ij} = 0 \quad \forall (i, j) \in \mathcal{C} \nonumber
\end{align}
%
By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy:
\begin{align}
  \sum  w_{ij} \cdot y^*_{ij}  \leq \min \left( \sum  w_{ij} \cdot y'_{ij} ,  \sum   w_{ij} \cdot y''_{ij} \right)
\end{align}
%
Eq.~\ref{eq:fusion_move_a} can be solved efficiently, since 
we can work on a coarser graph, where all nodes which are connected
via must-link constraints are merged into single nodes.
This coarser graph is constructed by contracting all must-link edges.
